Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-24 scnn.tex
adding refs

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx,array}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{bm}

@@

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx,array}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{bm}
\usepackage{aasmacros}

@@

Cosmological data often comes in a form of spherical sky maps.
Observables such as the Cosmic Microwave Background (CMB) \citep{planck2015cosmologicalparameters,komatsu2011sevenyear,staggs2018recentdiscoveries}, neutral hydrogen \citep{santos2015cosmologySKA,HI4PI2016fullskyHI}, galaxy clustering \citep{alam2017clusteringgalaxies}, gravitational lensing \citep{troxel2017darkenergy,hildebrandt2017kidscosmological}, and others have been used to constrain cosmological models

Cite the following papers:
\begin{itemize}
    \item Healpix paper \citep{gorski2005healpix}
    \item First DES mass maps \citep{chang2017curvedsky}
    \item Healpix convolutions with asymetric beams \citep{mitra2011fastpixel}
    \item Mass mapping on the sphere \citep{wallis2017mappingdark}
    \item Wavelets on the sphere \citep{leistedt2016wavelet}
    \item Planck main result \citep{planck2015cosmologicalparameters,komatsu2011sevenyear}
    \item HI map \citep{HI4PI2016fullskyHI,}
    \item more radio maps from Adam+Hamsa \citep{santos2015cosmologySKA}
    \item more astro science on the sphere, what other survey make maps?
    \item alternative sampling on the sphere \citep{mcewen2011novelsampling} MW sampling
    \item cite kids tomographic power spectrum \citep{koehlinger2017kidstomographic}
\end{itemize}
